Visualizing Functional Data

### 2016-12-23 sections/section0d.tex
table and conditionals
histograms and bars

\subsection{Univariate Observations}
%%histogram and pdfs/distribution fitting

The specific shape is
dependent on what sort of density estimation method is used, such as kernal
estimation or nearest neighbor estimation \cite{chambers1983}. 
width using the density-trace method-which is a probability density estimation
via moving windowed average) proposed by Chambers et. al \cite{chambers1983},.

>>>>

\subsection{Univariate Observations}

The bar graph is arguable the simplest way to visualize data that is all of the
same type drawn from a sample at random. In this visualization technique, the
heights of the bar are representative of the values, the x valuesare each
invidual observation and the positioning of the x values is somewhat
arbitrary. \cite{TufteVisualDIsplay, Friendly, Playfair}. Since bar
graphs become somewhat useless as the number of samples increase, it is common
to group (bin) the data and then count the number of elements in each
been. Both this binning and counting and the subsequent bar chart of the
frequency are referred to as histograms \cite{ioannidis2003}. While histograms
give an approximation of the distribution of the data, sometimes the bin widths
can be too wide and thereby fail to catch naunces in the data such as
bimodality. A way to counteract this is to build histograms with very thin
buckets, which is one of the less sophisticated methods of doing kernal density
estimation. Other methods of approximating the distribution include nearest
neighbor estimation or the  moving windowed average density trace method \cite{chambers1983}.
